---
title:  Intro to Conjoint Experiments | Exercise - 1
author: Alberto Stefanelli
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    use_bookdown: true
    fig_width: 12
    fig_height: 8
  #html_document:
    #theme: rmdformats
    # df_print: paged
    # toc: true
    # number_sections: true
    # toc_float:
    #   collapsed: false
    #   smooth_scroll: false
---
<style type="text/css">
#content {
    max-width: 1500px !important;
/*    !margin-left: 300px !important;
*/
}
#table-of-contents {
    width: 300px !important;
}

#postamble {
  font-size: 10px;
}

pre{
  background-color: #FFFFFF;
    font-size: 12px;
}
pre:not([class]) {
  background-color: #D8D8D8;
    color: black;
}

</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, 
  fig.show = 'hold', 
  fig.align = "center", 
  warning = FALSE, 
  message = FALSE, 
  comment = '')
options(width = 300, scipen = 9999)

# last dev version is needed for rmdformats.
# fixed these two
# more info https://github.com/juba/rmdformats/issues/92 
# more info https://github.com/juba/rmdformats/issues/93
# devtools::install_github("juba/rmdformats")

```

  
# Environment preparation 


```{r, echo=T, message=FALSE, warning=FALSE,cache=F}

# ### Data import ###
# install.packages("readr")     # read datasets
# install.packages("qualtRics") # read qualtrics datasets
# install.packages("here")      # absolute path management
# ### Data manipulation ###
# install.packages("dplyr")     # pipes and data manipulation
# ### Visualization ###
# install.packages("ggplot2")    # graphing capabilities
# ### Estimation ###
# install.packages("cjoint")    # base amce package
# install.packages("cregg")     # amce and mm 
# install.packages("factorEx")  # amce with non-uniform distribution

## Custom build functions 
# library(devtools)
# install_github("albertostefanelli/cjoint") # fixes some problem with cjoint

### Data import ###
library("readr")     
library("qualtRics") 
library("here")
### Data manipulation ###
library("dplyr")     
### Visualization ###
library("ggplot2")    
### Estimation ###
library("cjoint")   
library("cregg")     
library("factorEx")  



```

# Data 

We are going to use the data from Kirkland, Patricia A; Coppock, Alexander, 2017, "Replication Data for: Candidate Choice Without Party Labels: New Insights from Conjoint Survey Experiments", https://doi.org/10.7910/DVN/WSUHI3. 

# Codebook

The data has no codebook so we need to load it and understand how it is structured.

# Exercise 1 

1. Load the data 
2. What's the sample size?
3. What the variable contest_no refers to?
4. How can the respondent-varying characteristics can be identified?
5. Do we have any info on the 'quality' of the data?
6. What's the main difference between how the data is organized here and the one presented in the Lab 1?


```{r, echo=T, message=FALSE, warning=FALSE}

kc_data <- readr::read_csv("https://github.com/albertostefanelli/conjoint_class/raw/master/data/Kirkland_Coppock_mturk_replication.csv")

```




