---
title:  Intro to Conjoint Experiments | Solutions - 4
author: Alberto Stefanelli
bibliography: /Users/serg/Library/Mobile Documents/com\~apple\~CloudDocs/academia/library.bib
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    use_bookdown: true
    fig_width: 12
    fig_height: 8
  #html_document:
    #theme: rmdformats
    # df_print: paged
    # toc: true
    # number_sections: true
    # toc_float:
    #   collapsed: false
    #   smooth_scroll: false
---
<style type="text/css">
#content {
    max-width: 1500px !important;
/*    !margin-left: 300px !important;
*/
}
#table-of-contents {
    width: 300px !important;
}

#postamble {
  font-size: 10px;
}

pre{
  background-color: #FFFFFF;
    font-size: 12px;
}
pre:not([class]) {
  background-color: #D8D8D8;
    color: black;
}

</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, 
  fig.show = 'hold', 
  fig.align = "center", 
  warning = FALSE, 
  message = FALSE, 
  comment = '')
options(width = 300, scipen = 9999)

# last dev version is needed for rmdformats.
# fixed these two
# more info https://github.com/juba/rmdformats/issues/92 
# more info https://github.com/juba/rmdformats/issues/93
# devtools::install_github("juba/rmdformats")

```

  
# Environment preparation 


```{r, echo=T, message=FALSE, warning=FALSE,cache=F}

# ### Data import ###
# install.packages("readr")     # read datasets
# install.packages("qualtRics") # read qualtrics datasets
# ### Data manipulation ###
# install.packages("dplyr")     # pipes and data manipulation
# ### Visualization ###
# install.packages("ggplot2")    # graphing capabilities
# ### Estimation ###
# install.packages("cjoint")    # base amce package
# install.packages("cregg")     # amce and mm 
# install.packages("factorEx")  # amce with non-uniform distribution

## Custom build functions 
# library(devtools)
# install_github("albertostefanelli/cjoint") # fixes some problem with cjoint

### Data import ###
library("readr")     
library("qualtRics") 
### Data manipulation ###
library("dplyr")     
### Visualization ###
library("ggplot2")    
### Estimation ###
library("cjoint")   
library("cregg")     
library("factorEx")  



```

# Data

1. From the paper "The Ties that Double Bind" [@teele_ties_2018]
2. We are going to use the Legislators and Voters sample
3. The authors want to test different type of gender biases
    - Among Legislators
    - Among Voters 

Attribute | Values
------------------ | ------------------------------------------------
Gender | Female, Male
Age | 29, 45, 65
Number of Children | 0, 1, 3
Highest Elected Political Post | None, Mayor, State Legislator
Occupation | Corporate Lawyer, Third Grade Teacher
Spouse's Occupation | Doctor, Farmer, Unmarried

- Variables in the dataset
    - CJ choice task= "winner"         
    - Type of sample = "sample"
    - Respondent's gender="female_respondent"  
    - Respondent's PID= "democrat_respondent", "republican_respondent"                       
    - Candidate's gender= "orig_cand_female"          
    - Candidate's political Experience= "orig_0ys", "orig_1ys", "orig_3ys", "orig_8ys"
    - Candidate's number of Children= "orig_0ch",  "orig_1ch",  "orig_3ch"  
    - Candidate's political Post= "orig_may", "orig_leg"                
    - Candidate's occupation= "orig_law", "orig_teach"                                     
    - Candidate's spouse's Occupation= "orig_UN_sp", "orig_FM_sp", "orig_MD_sp"                   
    - Candidate's candidate's Age= "orig_29", "orig_45", orig_65"          


# Task 

1. Postulate Hypothesises/Expectation
1. Estimate the AMCE for the candidates' traits
    - See if your Hypothesises/Expectation hold 
2. Re-estimate the AMCE using a simple OLS 
    - What happened? Please explain
3. [OPTIONAL] Estimate the AMCE in the voter sample 
    - Are there any differences?
4. Plot the results from the 
5. Test for respondent's fatigue 


```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}
# load the data 
teele_data <- readr::read_csv("https://github.com/albertostefanelli/conjoint_class/raw/master/data/teele.csv")

```


# Hypothesises

Let's first postulate some hypotheses 
- H1 There will be bias towards female candidates among legislators
- H2 Voters will be more biased towards female candidates compared to legislators

Let's estimate the AMCE for using the Teele Data. 

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}
# subset only legislators
data_teele_legislator <- subset(teele_data, sample == "usa leg")
# since there run a replication sample 2 years later, we are going to subset only the observations of the original sample 
data_teele_legislator <- subset(data_teele_legislator, replication == 0)
# let's now tranform all the variables related to the conjoint table into factor 
# they all start with c_ so it is easy to select them with the starts_with function 
data_teele_legislator <- data_teele_legislator %>% mutate_at(vars(starts_with("c_")),as.factor)

# run the amce and take into account the clustering 
amce_leg <- cjoint::amce(winner ~ 
     c_gender +
     c_experience+
     c_childern+
     c_occupation+
     c_age+
     c_spouse_occupation,
     data = data_teele_legislator, 
     cluster=TRUE,
     respondent.id="responseid")

summary(amce_leg)
```

Out hypothesis is disconfirmed. Changing the gender from Female to Male reduce by 0.11 percentage point the propensity to vote for a candidate.

# OLS 

Let's now run a simple regression model and see what happens. 

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}

lm_leg <- lm(winner ~ 
     c_gender +
     c_experience+
     c_childern+
     c_occupation+
     c_age+
     c_spouse_occupation,
     data = data_teele_legislator)

summary(lm_leg)

```

The coefficients are close to equivalence but the SE are off. The reason lies in the fact that with a simple OLS model we are not taking into account the clustering structure of the data (tasks nested into individuals). 

# Estimate the AMCE in the voter sample and test for differecnes

Let's turn to H2 and see if there is any difference between legislators and voters. 

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}
# all the same apart from the fact that in the first line we are selecting the voter sample  
data_teele_voters <- subset(teele_data, sample == "usa voter")
data_teele_voters <- subset(data_teele_voters, replication == 0)
data_teele_voters <- data_teele_voters %>% mutate_at(vars(starts_with("c_")),as.factor)

amce_voters <- cjoint::amce(winner ~ 
     c_gender +
     c_experience+
     c_childern+
     c_occupation+
     c_age+
     c_spouse_occupation,
     data = data_teele_voters, 
     cluster=TRUE,
     respondent.id="responseid")

summary(amce_voters)


```

There seems to be differences. In the voter sample our estimate is still negative but we go from 11% to 3%. Voters are, on average, less sensitive to the gender of the candidate compared to legislators (elite discourse?). Let's see if this difference is statistically significant.   


```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}

# let's test difference in AGE 45 VS AGE 29 with a simplified delta method
d<-amce_leg$estimates$cage["AMCE",][1] - amce_voters$estimates$cage["AMCE",][1]
var_leg<-amce_leg$estimates$cage["Std. Error",][1]^2 
var_voter<-amce_voters$estimates$cage["Std. Error",][1]^2 

ztest<- d / sqrt(var_leg+var_voter)
1-pnorm(ztest)

ifelse(1-pnorm(ztest) <0.05, "There are differences", "No differences")


```

# Plotting 


```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}

plot(amce_leg) +  scale_colour_grey(start = 0, end = .5) +
  theme_bw() + theme(text = element_text(size=18)) + 
    theme(legend.position = "none")

```

# Fatigue  

Let's now take a look at the effect of task on selecting a profile. We might expect that people got tired with the progression of the experiment and as such, we would see an effect of task progression on their response behaviour. Again, we want the coefficients to overlap to have no significant different between tasks. 

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}
data_teele_legislator$contest <- as.factor(data_teele_legislator$contest)

fit_fatigue <- cregg::cj(data_teele_legislator, winner ~ 
     c_gender +
     c_experience+
     c_childern+
     c_occupation+
     c_age+
     c_spouse_occupation,
     id = ~responseid,
     by = ~contest,
     estimate = "mm")

```

Let's now take a look at the effect of task on selecting a profile. We might expect that people got tired with the progression of the experiment and as such, we would see an effect of task numbering on their response behaviour. Again, we want the coefficients to overlap to have no significant different between tasks. 

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}
plot(fit_fatigue,
  group = "contest", vline = 0.5) + 
  theme(text = element_text(size=21))
```
Most of the MM overlap and we do not observe a clear pattern from the table. This means that respondents have not changed the way they make choices throughout the experiment. We can say that the respondent's fatigue is likely to be limited in the context of this experiment. 

# References {.allowframebreaks} 

