---
title:  Intro to Conjoint Experiments | Exercise - 5
author: Alberto Stefanelli
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
bibliography: /Users/serg/Library/Mobile Documents/com\~apple\~CloudDocs/academia/library.bib
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    use_bookdown: true
    fig_width: 12
    fig_height: 8
  #html_document:
    #theme: rmdformats
    # df_print: paged
    # toc: true
    # number_sections: true
    # toc_float:
    #   collapsed: false
    #   smooth_scroll: false
---
<style type="text/css">
#content {
    max-width: 1500px !important;
/*    !margin-left: 300px !important;
*/
}
#table-of-contents {
    width: 300px !important;
}

#postamble {
  font-size: 10px;
}

pre{
  background-color: #FFFFFF;
    font-size: 12px;
}
pre:not([class]) {
  background-color: #D8D8D8;
    color: black;
}

</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, 
  fig.show = 'hold', 
  fig.align = "center", 
  warning = FALSE, 
  message = FALSE, 
  comment = '')
options(width = 300, scipen = 9999)

# last dev version is needed for rmdformats.
# fixed these two
# more info https://github.com/juba/rmdformats/issues/92 
# more info https://github.com/juba/rmdformats/issues/93
# devtools::install_github("juba/rmdformats")

```

  
# Environment preparation 


```{r, echo=T, message=FALSE, warning=FALSE,cache=F}

# ### Data import ###
# install.packages("readr")     # read datasets
# install.packages("qualtRics") # read qualtrics datasets
# ### Data manipulation ###
# install.packages("dplyr")     # pipes and data manipulation
# ### Visualization ###
# install.packages("ggplot2")    # graphing capabilities
# ### Estimation ###
# install.packages("cjoint")    # base amce package
# install.packages("cregg")     # amce and mm 
# install.packages("factorEx")  # amce with non-uniform distribution

## Custom build functions 
# library(devtools)
# install_github("albertostefanelli/cjoint") # fixes some problem with cjoint

### Data import ###
library("readr")     
library("qualtRics") 
### Data manipulation ###
library("dplyr")     
### Visualization ###
library("ggplot2")    
### Estimation ###
library("cjoint")   
library("cregg")     
library("factorEx")  



```

# Data

1. From the paper "The Ties that Double Bind" [@teele_ties_2018]
2. We are going to use the Legislators and Voters sample
3. The authors want to test different type of gender biases
    - Among Legislators
    - Among Voters 

Attribute | Values
------------------ | ------------------------------------------------
Gender | Female, Male
Age | 29, 45, 65
Number of Children | 0, 1, 3
Highest Elected Political Post | None, Mayor, State Legislator
Occupation | Corporate Lawyer, Third Grade Teacher
Spouse's Occupation | Doctor, Farmer, Unmarried

- Variables in the dataset
    - CJ choice task= "winner"         
    - Type of sample = "sample"
    - Respondent's gender="female_respondent"  
    - Respondent's PID= "democrat_respondent", "republican_respondent"                       
    - Candidate's gender= "orig_cand_female"          
    - Candidate's political Experience= "orig_0ys", "orig_1ys", "orig_3ys", "orig_8ys"
    - Candidate's number of Children= "orig_0ch",  "orig_1ch",  "orig_3ch"  
    - Candidate's political Post= "orig_may", "orig_leg"                
    - Candidate's occupation= "orig_law", "orig_teach"                                     
    - Candidate's spouse's Occupation= "orig_UN_sp", "orig_FM_sp", "orig_MD_sp"                   
    - Candidate's candidate's Age= "orig_29", "orig_45", orig_65"          


# Task 

1. Attributes' interactions for the legislators sample 
    - Postulate Hypothesises/Expectation about attributes interactions
    - Test your hypothesises
    - Estimate the least-liked profile 
2. Sub-group analysis for the legislators sample 
    - Postulate Hypothesises/Expectation about subgroups 
    - Test your hypothesises
    - Estimate the least-liked profile 
3. Estimate a model with a non-uniform marginal distribution (data taken from legislatoR)
    - Gender .4, .6
    - Experience .2, .30, .3, .2
    - Children .33, .33, .33 
    - Occupation .10, .60, .20, .10
    - Spouse's Occupation .33, .33, .33
    - Age .20, .55, .25
4. Try replicate the sub-group analysis using a mixture model [OPTIONAL]
    - Include a concomitant variable in the estimation of the mixture components


```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}
# load the data 
teele_data <- readr::read_csv("https://github.com/albertostefanelli/conjoint_class/raw/master/data/teele.csv")

```

# References {.allowframebreaks} 
