---
title:  Intro to Conjoint Experiments | Lab - 4
author: Alberto Stefanelli
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    use_bookdown: true
    fig_width: 12
    fig_height: 8
  #html_document:
    #theme: rmdformats
    # df_print: paged
    # toc: true
    # number_sections: true
    # toc_float:
    #   collapsed: false
    #   smooth_scroll: false
---
<style type="text/css">
#content {
    max-width: 1500px !important;
/*    !margin-left: 300px !important;
*/
}
#table-of-contents {
    width: 300px !important;
}

#postamble {
  font-size: 10px;
}

pre{
  background-color: #FFFFFF;
    font-size: 12px;
}
pre:not([class]) {
  background-color: #D8D8D8;
    color: black;
}

</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, 
  fig.show = 'hold', 
  fig.align = "center", 
  warning = FALSE, 
  message = FALSE, 
  comment = '')
options(width = 300, scipen = 9999)

# last dev version is needed for rmdformats.
# fixed these two
# more info https://github.com/juba/rmdformats/issues/92 
# more info https://github.com/juba/rmdformats/issues/93
# devtools::install_github("juba/rmdformats")

```

# What we are going to do in this LAB

1. Get the data ready for CJ Analysis 
    - Descriptives
    - From Wide to Long
2. Perform the analysis in R
    1. AMCE 
3. Plotting 


## Dataset used 

1. 2018 CEU Experimental Political Science dataset
  1. Q578 Q579 Q580: Choice CJ Task 
  2. F-\*-\*: Conjoint features 
  3. Q78: Employment status
  4. Q77: Race 
  5. Q76: Education 
  6. Q75: Gender 
  7. Q74: Age 
  8. Q581: Religiosity

2. The Hidden American Immigration Consensus @hainmueller_causal_2014 
  1. Conditional AMCEs 
  2. Subgroups differences
  
    
# Environment preparation 


```{r, echo=T, message=FALSE, warning=FALSE,cache=F}

# ### Data import ###
# install.packages("readr")     # read datasets
# install.packages("qualtRics") # read qualtrics datasets
# ### Data manipulation ###
# install.packages("dplyr")     # pipes and data manipulation
# ### Visualization ###
# install.packages("ggplot2")    # graphing capabilities
# ### Estimation ###
# install.packages("cjoint")    # base amce package
# install.packages("cregg")     # amce and mm 
# install.packages("factorEx")  # amce with non-uniform distribution

## Custom build functions 
# library(devtools)
# install_github("albertostefanelli/cjoint") # fixes some problem with cjoint

### Data import ###
library("readr")     
library("qualtRics") 
### Data manipulation ###
library("dplyr")     
### Visualization ###
library("ggplot2")    
### Estimation ###
library("cjoint")   
library("cregg")     
library("factorEx")  



```


# Load the data: Qualtrics

- Let's take a look to how to deal with the Qualtrics format  
  - Qualtrics include HTML tags that are use for diagnostics 
  - We need to get rid of them 
  - We are going to use the **qualtRics** package for removing the tags

```{r, echo=T, message=FALSE, warning=FALSE}

df_base <- qualtRics::read_survey(here("data", "experimental_political_science_2019.csv"), # name of our data file
    legacy=FALSE,     # new or old version of Qualtrics 
    strip_html=TRUE   # remove the html tag
)

head(df_base)

```

