---
title:  Intro to Conjoint Experiments | Solutions - 1
author: Alberto Stefanelli
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    use_bookdown: true
    fig_width: 12
    fig_height: 8
  #html_document:
    #theme: rmdformats
    # df_print: paged
    # toc: true
    # number_sections: true
    # toc_float:
    #   collapsed: false
    #   smooth_scroll: false
---
<style type="text/css">
#content {
    max-width: 1500px !important;
/*    !margin-left: 300px !important;
*/
}
#table-of-contents {
    width: 300px !important;
}

#postamble {
  font-size: 10px;
}

pre{
  background-color: #FFFFFF;
    font-size: 12px;
}
pre:not([class]) {
  background-color: #D8D8D8;
    color: black;
}

</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, 
  fig.show = 'hold', 
  fig.align = "center", 
  warning = FALSE, 
  message = FALSE, 
  comment = '')
options(width = 300, scipen = 9999)

# last dev version is needed for rmdformats.
# fixed these two
# more info https://github.com/juba/rmdformats/issues/92 
# more info https://github.com/juba/rmdformats/issues/93
# devtools::install_github("juba/rmdformats")

```

  
# Environment preparation 


```{r, echo=T, message=FALSE, warning=FALSE,cache=F}

# ### Data import ###
# install.packages("readr")     # read datasets
# install.packages("qualtRics") # read qualtrics datasets
# install.packages("here")      # absolute path management
# ### Data manipulation ###
# install.packages("dplyr")     # pipes and data manipulation
# ### Visualization ###
# install.packages("ggplot2")    # graphing capabilities
# ### Estimation ###
# install.packages("cjoint")    # base amce package
# install.packages("cregg")     # amce and mm 
# install.packages("factorEx")  # amce with non-uniform distribution

## Custom build functions 
# library(devtools)
# install_github("albertostefanelli/cjoint") # fixes some problem with cjoint

### Data import ###
library("readr")     
library("qualtRics") 
library("here") 
### Data manipulation ###
library("dplyr")     
### Visualization ###
library("ggplot2")    
### Estimation ###
library("cjoint")   
library("cregg")     
#library("factorEx")  



```

# Data 

We are going to use the data from Kirkland, Patricia A; Coppock, Alexander, 2017, "Replication Data for: Candidate Choice Without Party Labels: New Insights from Conjoint Survey Experiments", https://doi.org/10.7910/DVN/WSUHI3. The data has no codebook so we need to load it and understand how it is structured. 

# Exercise 1 

1. Load the data 
2. What's the sample size?
3. What the variable contest_no refers to?
4. How can the respondent-varying characteristics can be identified?
5. Do we have any info on the 'quality' of the data?
6. What's the main difference between how the data is organized here and the one presented in the Lab 1?


```{r, echo=T, message=FALSE, warning=FALSE}

kc_data <- readr::read_csv("https://github.com/albertostefanelli/conjoint_class/raw/master/data/Kirkland_Coppock_mturk_replication.csv")

head(kc_data)
```


As we will see, in conjoint experiments, we need to distinguish between the number of respondents, number of task performed by each respondent, and the number of profiles shown in the conjoint task. 

The number or rows is the total number of observations uses for the analysis.

```{r, echo=T, message=FALSE, warning=FALSE}
nrow(kc_data)

```

To know the number of respondents we need to divide this number by the number of conjoint tasks and the number of profiles. 


```{r, echo=T, message=FALSE, warning=FALSE}
# number or tasks 
unique(kc_data$contest_no)
# number or profiles 
table(kc_data$contest_no,kc_data$win)
(respndents <- 12032/5/2)

```

```{r, echo=T, message=FALSE, warning=FALSE}
# number or tasks 
unique(kc_data$contest_no)
# number or profiles 
table(kc_data$contest_no,kc_data$win)
(respndents <- 12032/5/2)

```

In this case, we have only 1 respondent-varying characteristic that is its PID. 

```{r, echo=T, message=FALSE, warning=FALSE}

kc_data |> dplyr::select(dplyr::starts_with("resp_"))

```


# Design info (reconstructed)

 | Value
------------------ | ------------------------------------------------
Sample Size | 1203
N Tasks (contest_no) | 5
N Profiles | 2
Total Obs. | 12,032

# Codebook (reconstructed)

Variable | Value
------------------ | ------------------------------------------------
contest_no | CJ task
win | Profile chosen
Gender | CJ Attribute
Age | CJ Attribute
Job | CJ Attribute
Political | CJ Attribute
Job | CJ Attribute
Party | CJ Attribute
resp_mturkid | Respondent ID
resp_pid_7 | Strength PID (1. Strong Dem -- 7. Strong Rep)
resp_pid_3_text | PID (Democrat, Pure Independent, Republican)
same_party | whether R identify with the same party as in the candidate in the CJ 
comp | ?? 
policy_index | ?? 
valence_index | ?? 

