---
title:  Intro to Conjoint Experiments | Exercise - 5
author: Alberto Stefanelli
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
bibliography: /Users/serg/Library/Mobile Documents/com\~apple\~CloudDocs/academia/library.bib
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    use_bookdown: true
    fig_width: 12
    fig_height: 8
  #html_document:
    #theme: rmdformats
    # df_print: paged
    # toc: true
    # number_sections: true
    # toc_float:
    #   collapsed: false
    #   smooth_scroll: false
---
<style type="text/css">
#content {
    max-width: 1500px !important;
/*    !margin-left: 300px !important;
*/
}
#table-of-contents {
    width: 300px !important;
}

#postamble {
  font-size: 10px;
}

pre{
  background-color: #FFFFFF;
    font-size: 12px;
}
pre:not([class]) {
  background-color: #D8D8D8;
    color: black;
}

</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, 
  fig.show = 'hold', 
  fig.align = "center", 
  warning = FALSE, 
  message = FALSE, 
  comment = '')
options(width = 300, scipen = 9999)

# last dev version is needed for rmdformats.
# fixed these two
# more info https://github.com/juba/rmdformats/issues/92 
# more info https://github.com/juba/rmdformats/issues/93
# devtools::install_github("juba/rmdformats")

```

  
# Environment preparation 


```{r, echo=T, message=FALSE, warning=FALSE,cache=F}

# ### Data import ###
# install.packages("readr")      # read datasets
# install.packages("qualtRics")  # read qualtrics datasets
# ### Data manipulation ###
# install.packages("dplyr")      # pipes and data manipulation
# install.packages("stringr")     # text manipulation
# ### Visualization ###
# install.packages("ggplot2")    # graphing capabilities
# install.packages("ggimage")    # integrating images in ggplot
# ### Estimation ###
# install.packages("cjoint")     # base amce package
# install.packages("cregg")      # amce and mm 
# install.packages("factorEx")   # amce with non-uniform distribution
# install.packages("flexmix")    # mixture models 

## Custom build functions 
# library(devtools)
# devtools::install_github("albertostefanelli/cjoint") # fixes some problem with cjoint

### Data import ###
library("readr")     
library("qualtRics") 
### Data manipulation ###
library("dplyr")     
library("stringr")     
### Visualization ###
library("ggplot2")    
library("ggimage")
### Estimation ###
library("cjoint")   
library("cregg")     
library("factorEx") 
library("flexmix")


```

# Data

1. From the paper "The Ties that Double Bind" [@teele_ties_2018]
2. We are going to use the Legislators and Voters sample
3. The authors want to test different type of gender biases
    - Among Legislators
    - Among Voters 

Attribute | Values
------------------ | ------------------------------------------------
Gender | Female, Male
Age | 29, 45, 65
Number of Children | 0, 1, 3
Highest Elected Political Post | None, Mayor, State Legislator
Occupation | Corporate Lawyer, Third Grade Teacher
Spouse's Occupation | Doctor, Farmer, Unmarried

- Variables in the dataset
    - CJ choice task= "winner"         
    - Type of sample = "sample"
    - Respondent's gender="female_respondent"  
    - Respondent's PID= "democrat_respondent", "republican_respondent"                       
    - Candidate's gender= "orig_cand_female"          
    - Candidate's political Experience= "orig_0ys", "orig_1ys", "orig_3ys", "orig_8ys"
    - Candidate's number of Children= "orig_0ch",  "orig_1ch",  "orig_3ch"  
    - Candidate's political Post= "orig_may", "orig_leg"                
    - Candidate's occupation= "orig_law", "orig_teach"                                     
    - Candidate's spouse's Occupation= "orig_UN_sp", "orig_FM_sp", "orig_MD_sp"                   
    - Candidate's candidate's Age= "orig_29", "orig_45", orig_65"          


# Task

1. Attributes' interactions
    - Postulate Hypothesises/Expectation about attributes interactions
    - Test your hypothesises
    - Estimate the least-liked profile 
2. Sub-group analysis
    - Postulate Hypothesises/Expectation about subgroups 
    - Test your hypothesises
    - Estimate the least-liked profile 
3. Estimate a model with a non-uniform marginal distribution (data taken from legislatoR)
    - Gender .4, .6
    - Experience .2, .30, .3, .2
    - Children .33, .33, .33 
    - Occupation .10, .60, .20, .10
    - Spouse's Occupation .33, .33, .33
    - Age .20, .55, .25
4. Try to replicate the sub-group analysis using a mixture model [OPTIONAL]
    - Include a concomitant variable in the estimation of the mixture components

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}
# load the data 
teele_data <- readr::read_csv("https://github.com/albertostefanelli/conjoint_class/raw/master/data/teele.csv")

```

# Attributes' interactions

- **Expectation:** Candidates with high levels of experience and high number of children will be less likely to be chosen by the respondents (traditional family roles) 

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}

# let's recode the PID of the respondent
teele_data$r_PID <- as.factor(teele_data$r_PID) 
# let's recode the factor levels
teele_data <- teele_data %>% 
  mutate_at(vars(starts_with("c_")), as.factor)

interaction_attributes <- cjoint::amce(winner ~ 
     c_gender +
     c_experience * c_childern+
     c_childern+
     c_occupation +
     c_age+
     c_spouse_occupation,
     data = teele_data, 
     cluster=TRUE,
     respondent.id="responseid")

summary(interaction_attributes)
```

As hypothesised, there is an interaction effect between the number of children and political experience. This means that respondents evaluate the experience of the candidate differently depending on the number of children they have. For instance, having a candidate with 8 years of experience and 3 children VS a candidate without experience and without children decreases the probability of choosing that profile by 15 percentage point. We might want to select a different reference category to make our results more interpretable. For instance, I might be interested in keeping the number of children constant (3) and testing how political experience impact on the likelihood to select a profile.  


```{r, echo=T, cache=TRUE, message=FALSE, warning=FALSE,eval=TRUE}

least_liked <- cjoint::amce(
     winner ~ c_gender * c_experience * c_childern * c_occupation * c_age * c_spouse_occupation,
     data = teele_data, 
     cluster=TRUE,
     respondent.id="responseid")

summary(least_liked)
```

# Sub-group analysis

- **Expectation:** Democratic respondents will be more less responsive to the gender of the candidate compared to Republican respondents

Next we are going to see if Democrats VS Republicans and Male VS Female have different utility functions when it comes to candidate favourability. We refers to this phenomena as heterogeneity of the casual effect. 

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE}

interaction_PID <- cjoint::amce(winner ~ 
     c_gender * r_PID +
     c_experience+
     c_childern+
     c_occupation+
     c_age+
     c_spouse_occupation,
     data = teele_data, 
     cluster=TRUE,
     respondent.varying="r_PID",
     respondent.id="responseid")


summary(interaction_PID)

```

As anticipated, the gender of the candidate really matters for Democrats while it is non-significant for Republican. This is a very interesting finding and suggests that Democrats are the main driver behind our pooled sample result. 

# Non-uniform marginal distribution

Let's now include a non-uniform distribution of candidates' attributes 

- Marginal distribution 
    - Gender .4, .6
    - Experience .2, .30, .3, .2
    - Children .33, .33, .33 
    - Occupation .10, .60, .20, .10
    - Spouse's Occupation .33, .33, .33
    - Age .20, .55, .25

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE,cache=TRUE}

# Let's manually input the non-uniform distribution 
non_uniform_distribution <- c()
non_uniform_distribution[["c_gender"]] <- c(Female=.4,Male=.6)
non_uniform_distribution[["c_experience"]] <- c(orig_0ys=.2, orig_1ys=.30, orig_3ys=.3, orig_8ys=.2)
non_uniform_distribution[["c_childern"]] <- c(orig_0ch=.33333333, orig_1ch=.33333333, orig_3ch=.33333333)
non_uniform_distribution[["c_occupation"]] <- c(orig_teach=.10, orig_law=.60, orig_may=.20, orig_leg=.10)
non_uniform_distribution[["c_age"]] <- c(orig_29=.20, orig_45=.55, orig_65=.25)
non_uniform_distribution[["c_spouse_occupation"]] <- c(orig_UN_sp=.33333333, orig_FM_sp=.33333333, orig_MD_sp=.33333333)

# Let's select only the relevant variable since the model_pAMCE function does not accept NAs 

subset_teele <-  teele_data %>%
    dplyr::select(winner, 
     c_gender,
     c_experience,
     c_childern,
     c_occupation,
     c_age,
     c_spouse_occupation,
     responseid)

# remove all NAs
subset_teele_wo_NA <- na.omit(subset_teele)
# the model_pAMCE is very strict with the naming so we need to change class to our data.frame
class(subset_teele_wo_NA) <-"data.frame"

model_marginal <- model_pAMCE(
     formula = winner ~ 
     c_gender +
     c_experience+
     c_childern+
     c_occupation+
     c_age+
     c_spouse_occupation,
  data = subset_teele_wo_NA,
  reg =FALSE,
  cluster_id = subset_teele_wo_NA$responseid,
  target_dist = non_uniform_distribution, 
  target_type = "marginal",
  boot= 500, 
  numCores = 4, 
)

summary(model_marginal)
```

There are differences but, in this case, the fact that respondents are "biased" in favour of female candidates still holds (and the effect is even stronger). 

# Conjoint Mixture Model 

```{r, echo=T, message=FALSE, warning=FALSE,eval=TRUE,cache=TRUE}

subset_teele <-  teele_data %>%
    dplyr::select(winner, 
     c_gender,
     c_experience,
     c_childern,
     c_occupation,
     c_age,
     c_spouse_occupation,
     responseid,
     female_respondent)

subset_teele_wo_NA <- subset_teele %>% 
  mutate_at(vars(starts_with("c_"), responseid), as.factor) %>% 
  mutate_at(vars(starts_with("c_"), responseid), droplevels) %>%
  data.frame() %>%
  na.omit()


formula  <- winner ~ c_gender + c_experience+ c_childern + c_occupation + c_age+ c_spouse_occupation | responseid



# Model without concomitant variables
set.seed(1402)

fmod0 <- flexmix::flexmix(formula, data = subset_teele_wo_NA, k = 2,
                 model = FLXglm(family = "gaussian"),
                 concomitant = FLXPmultinom(~ female_respondent)
                 )

# we need re-fit the model to obtain sd. errors 
rfmod0 <- refit(fmod0)
fit_3 <- summary(rfmod0)

fit_3


```

The coefficient for gender is similar to the one obtained in the sub-group analysis model. In addition, we strong effect heterogeneity across the two classes. We might speculate that Component 1 resemble democratic voter while Component 2 Republican identifiers. 


# References {.allowframebreaks} 
